---
title: "K-Means"
author: "JK"
date: "5/9/2019"
output: html_document
---


K-Means clustering makes clusters based on minimizing intra-cluster variation

standard algorithm defines the total within-cluster variation as the sum of squared distances Euclidean distances between items and the corresponding centroid:

W(Ck)=∑xi∈Ck(xi−μk)2

where:

xi is a data point belonging to the cluster Ck
μk is the mean value of the points assigned to the cluster Ck


1. Specify k - the number of clusters to be created.

2. Select randomly k objects from the dataset as the initial cluster centers.

3. Assign each observation to their closest centroid, based on the Euclidean distance    between the object and the centroid.

4. For each of the k clusters recompute the cluster centroid by calculating the new     mean value of all the data points in the cluster.

5. Iteratively minimize the total within sum of square. Repeat Step 3 and Step 4,       until the centroids do not change or the maximum number of iterations is reached     (R uses 10 as the default value for the maximum number of iterations).

kmeans(x=dataframe, centers = # of clusters)


```{r}

Lat <- c(40.1, 40.2, 40.3, 40.4, 40.5, 41.1, 41.2, 41.3, 41.4, 41.5, 45.1, 45.2, 45.3, 45.4)
Lon <- c(-70.1, -70.2, -70.3, -70.4, -70.5, -71.1, -71.2, -71.3, -71.4, -71.5, -75.1, -75.2, -75.3, -75.4)
df1 <- cbind(Lat, Lon)
df1
```


```{r}

Map_clusters <- function(df, main_clusters, sub_clusters){

    clers <- kmeans(df, main_clusters)
      df2 <- cbind(df[,1], df[,2], clers$cluster)
      
      
  sub_clers <- vector("logical", length =100)
  
  for(i in 1:sub_clusters){
    
    sub_df <- subset(df2, df2[,3] == i)
    
      sub_clers[i] <- kmeans(sub_df[i], sub_clusters)
      
      
      df3[i] <- cbind(sub_df[,1][i], sub_df[,2][i], sub_df[,3][i], sub_clers$clusters[i])
      
    }
  
      
  df4 <- data.frame(df3)
  

  print(df4)
}

Map_clusters(df1, 3, 3)

```







